---
title: "README"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bfd)
```

## Big Frame o' Data

`bfd` is a small project that aims to handle big data. Big for memory, not for hard drives. It is mostly a learning
exercise but it may turn into something more useful. The `fst` package will hopefully fill the vacuum of R
packages that can chunk over on-disk data, but until then `bfd` is no big deal.

## Classes

`bfd` has a set of reference classes that handle writing and reading vectors of all R's base types. These are
created using the `make_bfdcol` generic function:

```{r}
data(iris)

unlink("iris.bin", TRUE, TRUE)

dir.create("iris.bin")
cols <- mapply(make_bfdcol, iris, names(iris), MoreArgs = list(path="iris.bin", write=TRUE))
```

The preceding code is a little inconvenient but a function to create a `bfd` from a `data.frame` is in the works.
It returns a list of `bfdcols` which contain the following information:

```{r}
cols[[1]]
```

## Reading from a `bfd`

Because the `bfdcol`s keep a reference to the binary file location, reading data back into R requires no further
arguments. Wrapping it in a `data.frame` produces the original dataset:

```{r}
d <- data.frame(lapply(cols, function(x) x$read()))

head(d)

all.equal(d, iris)

```


